---
title: "data"
author: "Zhiying Hu"
date: "2022-12-10"
output: html_document
---

```{r, comment=NA, include=FALSE, echo=FALSE}
packs.inst <- c("readxl","foreign","dplyr","tidyr","ggplot2","stargazer","haven","dummies","Hmisc","lmtest","sandwich", "doBy", "multiwayvcov", "miceadds", "car", "purrr", "knitr", "zoo", "readstata13", "tidyverse", "psych","wesanderson", "lubridate","reporttools", "data.table", "devtools","rmarkdown","estimatr", "ivpack", "Jmisc", "lfe", "plm", "tinytex", "xts", "psych", "PerformanceAnalytics","roll", "rollRegres", "glmnet", "hdm", "broom", "RCurl", "learnr", "maps", "fGarch", "remotes", "RPostgreSQL", "wrds", "DBI", "RPostgreSQL", "remotes", "RPostgres", "Rmisc", "ggthemes", "splitstackshape", "gginference", "MASS","fBasics","xtable")
packs.load <- c("fGarch")
# lapply(packs.inst, install.packages, character.only = FALSE) 
lapply(packs.inst, require, character.only = TRUE)
```

# Part 1: deal with the data
## import data
```{r}
# real inflation rate from monthly year-on-year CPI
CPI <- read.csv("~/Desktop/DTFF_final/data/CPI.csv")
# expected inflation rate from 1-year bond yield to maturity
bond <- read.csv("~/Desktop/DTFF_final/data/bond.csv")
# commodity futures' price data
commodity <- read.csv("~/Desktop/DTFF_final/data/commodity.csv")[-1,]
# stock and gold price
stock_gold <- read.csv("~/Desktop/DTFF_final/data/stock_gold.csv")[-1,]
# real estate price
realestate <- read.csv("~/Desktop/DTFF_final/data/real_estate.csv")
```
## time-series data
```{r}
dateymd <- as.Date(ymd(commodity[,1]))
CPI_ts <- xts(x = CPI[,-1], order.by = dateymd)
bond_ts <- xts(x = bond[,-1], order.by = dateymd)
commodity_ts <- xts(x = commodity[,-1], order.by = dateymd)
stock_gold_ts <- xts(x = stock_gold[,-1], order.by = dateymd)
realestate_ts <- xts(x = realestate[,-1], order.by = dateymd[18:156])
```
## merger the returns
```{r}
# calculate the monthly year-on-year logarithm yield
colnames(CPI_ts) <- "monthly year-on-year CPI"
CPI_log_ts <- log(1+CPI_ts[,1])
colnames(CPI_log_ts) <- "real_inflation" # from 2009-01
# 1-year bond t-1 the yield of maturity is used as the expected inflation rate at time t
bond_lag_ts <- stats::lag(bond_ts,1)
colnames(bond_lag_ts) <- "expected_inflation" # value from 2009-02
# monthly year-on-year logarithm yield of commodities
commodity_log_ts <- log(commodity_ts) - log(stats::lag(commodity_ts,12)) # from 2010-01, 12 values
# monthly year-on-year logarithm yield of stock and gold
stock_gold_log_ts <- log(stock_gold_ts) - log(stats::lag(stock_gold_ts,12)) # from 2010-01, 12 values
# monthly year-on-year logarithm yield of real estate
realestate_log_ts <- log(realestate_ts) - log(stats::lag(realestate_ts,12)) # from 2011-06, 12 values

CPI_log_ts <- CPI_log_ts[13:156,]
bond_lag_ts <- bond_lag_ts[13:156,]
commodity_log_ts <- commodity_log_ts[13:156,]
stock_gold_log_ts <- stock_gold_log_ts[13:156,]
unexpected_inflation <- CPI_log_ts - bond_lag_ts 
colnames(unexpected_inflation) <- "unexpected_inflation"
realestate_log_ts <- realestate_log_ts[13:139,]
DATA1 <- merge.xts(CPI_log_ts, bond_lag_ts, unexpected_inflation, commodity_log_ts, stock_gold_log_ts)
DATA2 <- merge.xts(CPI_log_ts[18:144], bond_lag_ts[18:144], unexpected_inflation[18:144], realestate_log_ts)
DATA3 <- merge.xts(CPI_log_ts, bond_lag_ts, unexpected_inflation, commodity_log_ts, stock_gold_log_ts, realestate_log_ts)
save(DATA3,file = "return.RData")
```

## Stationary Test: ADF Test
```{r}
# ADF test
library(tseries)
for (i in 1:ncol(DATA3)) {
  if (tseries::adf.test(na.omit(DATA3[,i]))$p.value < 0.05) 
    {cat(colnames(DATA3)[i], "is stationary series I(0) series", "\n")}
    else if (tseries::adf.test(na.omit(diff(DATA3[,i])))$p.value < 0.05) 
      {cat(colnames(DATA3)[i], "is first order integration series I(1) series","\n")}
      else
      cat("NULL","\n")}
```
```{r}
ADF_result <- c()
for (i in 1:ncol(DATA3)) {
  if (tseries::adf.test(na.omit(DATA3[,i]))$p.value < 0.05) 
    {ADF_result = c(ADF_result, "I(0)")}
    else if (tseries::adf.test(na.omit(diff(DATA3[,i])))$p.value < 0.05) 
      {ADF_result = c(ADF_result, "I(1)")}
      else
      ADF_result = c(ADF_result, "NULL")}

ADF_result <- as.data.frame(cbind(asset = colnames(DATA3),
                                  ADF_result))
ADF_result
```
# Part 2: Examination of the Inflation Hedging Ability
## regression of commodity futures
```{r}
## commodity futures
library(stargazer)
cm_lm1 =list()
for (i in 4:7) {
  cm_lm1[[i-3]]  <- lm(DATA3[,i] ~ DATA3$expected_inflation + DATA3$unexpected_inflation)}
cm_reg1 <- stargazer(cm_lm1, dep.var.labels = "asset", align = TRUE, df = FALSE)

cm_lm2 =list()
for (i in 8:11) {
  cm_lm2[[i-7]]  <- lm(DATA3[,i] ~ DATA3$expected_inflation + DATA3$unexpected_inflation)}
cm_reg2 <- stargazer(cm_lm2, dep.var.labels = "asset", align = TRUE, df = FALSE)

cm_lm3 =list()
for (i in 12:15) {
  cm_lm3[[i-11]]  <- lm(DATA3[,i] ~ DATA3$expected_inflation + DATA3$unexpected_inflation)}
cm_reg3 <- stargazer(cm_lm3, dep.var.labels = "asset", align = TRUE, df = FALSE)

cm_lm4 =list()
for (i in 16:19) {
  cm_lm4[[i-15]]  <- lm(DATA3[,i] ~ DATA3$expected_inflation + DATA3$unexpected_inflation)}
cm_reg4 <- stargazer(cm_lm4, dep.var.labels = "asset", align = TRUE, df = FALSE)
```
## regression of spot gold
```{r}
## spot gold
sg <- lm(DATA3$Gold_price ~ DATA3$expected_inflation + DATA3$unexpected_inflation)
sg_reg <- stargazer(sg, dep.var.labels = "Spot Gold", align = TRUE, df = FALSE)
```
## regression of industry stocks
```{r}
## industry stocks
stock_lm1 =list()
for (i in 21:25) {
  stock_lm1[[i-20]]  <- lm(DATA3[,i] ~ DATA3$expected_inflation + DATA3$unexpected_inflation)}
stock_reg1 <- stargazer(stock_lm1, dep.var.labels = "industry stocks", align = TRUE, df = FALSE)

stock_lm2 =list()
for (i in 26:30) {
  stock_lm2[[i-25]]  <- lm(DATA3[,i] ~ DATA3$expected_inflation + DATA3$unexpected_inflation)}
stock_reg2 <- stargazer(stock_lm2, dep.var.labels = "industry stocks", align = TRUE, df = FALSE)
```
## regression of real estate
```{r}
## real estate
estate_lm = list()
for (i in 31:33) {
  estate_lm[[i-30]]  <- lm(DATA3[,i] ~ DATA3$expected_inflation + DATA3$unexpected_inflation)}
estate_reg <- stargazer(estate_lm, dep.var.labels = "real estate", align = TRUE, df = FALSE)
```
## result of inflation hedging effect
```{r}
assetnames <- colnames(DATA3[,-(1:3)])
Expected   = c(assetnames[c(1,2,3,6,7,8,9,10,12,13,17,19,23,25,29,30)],NA)
Unexpected = assetnames[c(2,4,6,7,8,10,11,12,13,17,19,20,21,23,24,27,30)]
HedgingAbility <- cbind(Expected, Unexpected)
as.data.frame(HedgingAbility)
xtable(as.data.frame(HedgingAbility))
```

# Part 3: Inflation Hedgig Portfolio by Mean Variance Method
## exclude assets which have no inflation hedging effect
```{r}
asset_returns <- DATA3[,-c(1:3)]
asset_returns <- asset_returns[,-c(5,14,15,16,18,22,26,28)]
save(asset_returns, file="asset_returns.RData")
dim(asset_returns)
```
## the set of attainable portfolios
```{r}
# Calculate the mean vector and covariance matrix
mean_ret <- colMeans(asset_returns, na.rm = T)
cvar_ret <- cov(na.omit(asset_returns))

# Calculate individual weights 
for (i in colnames(asset_returns)[-(dim(asset_returns)[2])]) {
  weight = runif(10000, min=-1.5, max=1.5)
  names = paste0(i,"_weight")
  if (i == "soybeans.No..1"){
    weight_final = weight
    names_final = names}
  else {
    weight_final = cbind(weight_final, weight)
    names_final = cbind(names_final, names)}
  }

# Get the dataframe and matrix on the weights
weight_df <- as.data.frame(weight_final)
colnames(weight_df) <- names_final

weight_df$sum <- rowSums(weight_df)
weight_df$third.tier <- 1 - weight_df$sum 
weight_df$sum <- NULL

matrix_weights <- as.matrix(weight_df)

# report the weights of the matrix
data.frame(matrix_weights)

# Calculate the feasible expected returns and standard deviations
feasible_pf_mu = matrix_weights%*%mean_ret
feasible_pf_sd = apply(matrix_weights, 1, function(x) sqrt(t(x) %*% cvar_ret %*% x))

# Construct the feasible dataframe, consisting of 10000 differently weighted risk and return combinations
feasible_pf <- as.data.frame(cbind(feasible_pf_mu, feasible_pf_sd))  
colnames(feasible_pf) <- c("Portfolio_Return", "Portfolio_Risk")

# report the feasible dataframe
feasible_pf

# Now, let's visualise the relationship
feasible_pf %>% 
  ggplot(aes(x= Portfolio_Risk, y = Portfolio_Return)) + 
  geom_point(color = "grey") + 
  geom_point(data = subset(feasible_pf, Portfolio_Risk <= 0.12 & Portfolio_Return >= 0), color = "darkorchid3", shape = 1, aes(x= Portfolio_Risk, y = Portfolio_Return)) +
  geom_point(data = subset(feasible_pf, Portfolio_Risk > 0.12 & Portfolio_Risk <= 0.14 & Portfolio_Return >= 0.07), color = "darkorchid3", shape = 1,aes(x= Portfolio_Risk, y = Portfolio_Return)) +
  geom_point(data = subset(feasible_pf, Portfolio_Risk > 0.14 & Portfolio_Risk <= 0.16 & Portfolio_Return >= 0.09), color = "darkorchid3", shape = 1,aes(x= Portfolio_Risk, y = Portfolio_Return)) +
  geom_point(data = subset(feasible_pf, Portfolio_Risk > 0.16 & Portfolio_Risk <= 0.18 & Portfolio_Return >= 0.1), color = "darkorchid3", shape = 1,aes(x= Portfolio_Risk, y = Portfolio_Return)) +
  geom_point(data = subset(feasible_pf, Portfolio_Risk > 0.18 & Portfolio_Risk <= 0.20 & Portfolio_Return >= 0.11), color = "darkorchid3",shape = 1, aes(x= Portfolio_Risk, y = Portfolio_Return)) +
  geom_point(data = subset(feasible_pf, Portfolio_Risk > 0.2 & Portfolio_Risk <= 0.22 & Portfolio_Return >= 0.11), color = "darkorchid3", shape = 1, aes(x= Portfolio_Risk, y = Portfolio_Return)) +
  ylab(expression(mu[p])) + xlab(expression(sigma[p])) + ggtitle("Porfolio Frontier for 10'000 different weights") +
  labs(color='Factor Portfolios') +
  theme(plot.title= element_text(size=14, color="grey26",
  hjust=0.3,lineheight=2.4, margin=margin(15,0,15,0)), 
  panel.background = element_rect(fill="#f7f7f7"),
  panel.grid.major.y = element_line(size = 0.5, linetype = "solid", color = "grey"),
  panel.grid.minor = element_blank(),
  panel.grid.major.x = element_blank(),
  plot.background = element_rect(fill="#f7f7f7", color = "#f7f7f7"), 
  axis.title.y = element_text(color="grey26", size=12, margin=margin(0,10,0,10)),
  axis.title.x = element_text(color="grey26", size=12, margin=margin(10,0,10,0)),
  axis.line = element_line(color = "grey"))
```
## the minmum - variance portfolio
```{r}
# Define the matrix A. It consists of: 

## - the covariance matrix multiplied by two
## - a column right to the covariance matrix, consisting of 1's
## - a row right below the covariance matrix and the additional column, consisting of 1's and one zero (the zero is in the right-bottom of the resulting matrix)
mat_A <- rbind(cbind(2*cvar_ret, rep(1, dim(cvar_ret)[1])), 
               c(rep(1, dim(cvar_ret)[1]), 0))
# Define the vector b as vector of zeros with dimension of the covariance matrix (19 in this case) and one 1 at the bottom
vec_b <- c(rep(0, dim(cvar_ret)[1]), 1)
# Calculate the inverse and perform matrix multiplication to get the vector z
z <- solve(mat_A)%*%vec_b
# Derive the first N elements of the vector to retrieve the actual values 
x_MV <- z[1:dim(cvar_ret)[1]]
# Check that the sum adds up to 1
sum(x_MV)
```
```{r}
# Calculate the expected return: 
mu_MV <- x_MV %*% mean_ret
sd_MV <- sqrt(t(x_MV) %*% cvar_ret %*% x_MV)
# Create the appropriate dataframe
MV_PF <- as.data.frame(cbind(mu_MV, sd_MV, t(x_MV)))
colnames(MV_PF) <- c("Mu_MV", "Sd_MV",names_final, "third.tier_weight")
as.data.frame(t(MV_PF))
```

```{r}
# Now, let's visualize the relationship
feasible_pf %>% 
  ggplot(aes(x= Portfolio_Risk, y = Portfolio_Return)) + 
  geom_point(color = "grey") +
  # This is just to color in the "optimal PFs"
  geom_point(data = subset(feasible_pf, Portfolio_Risk <= 0.12 & Portfolio_Return >= 0.02), color = "darkorchid3", shape = 1, aes(x= Portfolio_Risk, y = Portfolio_Return)) +
  geom_point(data = subset(feasible_pf, Portfolio_Risk > 0.12 & Portfolio_Risk <= 0.14 & Portfolio_Return >= 0.07), color = "darkorchid3", shape = 1,aes(x= Portfolio_Risk, y = Portfolio_Return)) +
  geom_point(data = subset(feasible_pf, Portfolio_Risk > 0.14 & Portfolio_Risk <= 0.16 & Portfolio_Return >= 0.09), color = "darkorchid3", shape = 1,aes(x= Portfolio_Risk, y = Portfolio_Return)) +
  geom_point(data = subset(feasible_pf, Portfolio_Risk > 0.16 & Portfolio_Risk <= 0.18 & Portfolio_Return >= 0.1), color = "darkorchid3", shape = 1,aes(x= Portfolio_Risk, y = Portfolio_Return)) +
  geom_point(data = subset(feasible_pf, Portfolio_Risk > 0.18 & Portfolio_Risk <= 0.20 & Portfolio_Return >= 0.11), color = "darkorchid3",shape = 1, aes(x= Portfolio_Risk, y = Portfolio_Return)) +
  geom_point(data = subset(feasible_pf, Portfolio_Risk > 0.2 & Portfolio_Risk <= 0.22 & Portfolio_Return >= 0.11), color = "darkorchid3", shape = 1, aes(x= Portfolio_Risk, y = Portfolio_Return)) +
  # Calculate and plot the Minimum Variance PF
  geom_point(color = "goldenrod",  aes(x= MV_PF$Sd_MV, y = MV_PF$Mu_MV), size = 3) +
  annotate('text',x = -0.01 ,y = 0, label = "Minimum Variance PF", size = 3.5, color = "goldenrod") +
  ylab(expression(mu[p])) + xlab(expression(sigma[p])) + ggtitle("Minimum Variance portfolio") +
  labs(color='Factor Portfolios') +
  xlim(-0.10, 0.75) + 
  theme(plot.title= element_text(size=14, color="grey26",
  hjust=0.43,lineheight=2.4, margin=margin(15,0,15,0)), 
  panel.background = element_rect(fill="#f7f7f7"),
  panel.grid.major.y = element_line(size = 0.5, linetype = "solid", color = "grey"),
  panel.grid.minor = element_blank(),
  panel.grid.major.x = element_blank(),
  plot.background = element_rect(fill="#f7f7f7", color = "#f7f7f7"), 
  axis.title.y = element_text(color="grey26", size=12, margin=margin(0,10,0,10)),
  axis.title.x = element_text(color="grey26", size=12, margin=margin(10,0,10,0)),
  axis.line = element_line(color = "grey"))
```
## portfolio efficient frontier
```{r}
# First we calculate the first Efficient Portfolio
# Define the EW return
mu_spec_x <- mu_MV
mu_spec_y <- 0.1

# We first define again the Matrix A 
mat_A_EF <- rbind(cbind(2*cvar_ret, mean_ret,  rep(1,dim(cvar_ret)[1])), 
                  cbind(t(mean_ret), 0, 0), 
                  cbind(t(rep(1,dim(cvar_ret)[1])), 0, 0))

# Then, we define the vector b
vec_b_EF_x <- c(rep(0, dim(cvar_ret)[1]), mu_spec_x, 1)
vec_b_EF_y <- c(rep(0, dim(cvar_ret)[1]), mu_spec_y, 1)

# Now, we can solve for the respective weights
z_EF_x <- solve(mat_A_EF)%*%vec_b_EF_x
z_EF_y <- solve(mat_A_EF)%*%vec_b_EF_y

# Then, we take the first N elements to get the respective weights
x_EF <- z_EF_x[1:dim(cvar_ret)[1]]
y_EF <- z_EF_y[1:dim(cvar_ret)[1]]

# Now, let's calculate the risk
sd_EF_x <- sqrt(t(x_EF) %*% cvar_ret %*% x_EF)
sd_EF_y <- sqrt(t(y_EF) %*% cvar_ret %*% y_EF)
sd_EF_xy <- t(x_EF) %*% cvar_ret %*% y_EF
```

```{r}
# Lastly, compute the weights and results
a = seq(from=0, to=1, by=0.05) 
# Create the expected return as well as the variance and standard deviation of each portfolios
mu_z = a * mu_spec_x + (1-a) * mu_spec_y
sd_z = sqrt(a^2*sd_EF_x^2 + (1-a)^2*sd_EF_y^2 + 2*a*(1-a)*sd_EF_xy)
# Create a dataframe consisting of different weights
z = matrix(0, length(a), dim(asset_returns)[2]) 

for (i in 1:length(a)){
  z[i, ] = a[i]*x_EF + (1-a[i])*y_EF
  }

# Create a dataframe consisting of only the efficient linear transformation portfolios
z_df <- as.data.frame(cbind(mu_z, sd_z))
colnames(z_df) <- c("Efficient_PF_Return", "Efficient_PF_Risk")
```
```{r}
# Now, let's visualise the relationship
z_df %>% 
  ggplot(aes(x= Efficient_PF_Risk, y = Efficient_PF_Return), color = "goldenrod") + 
  geom_point() + 
  geom_path() + 
  ylab(expression(mu[p])) + xlab(expression(sigma[p])) + ggtitle("The Portfolio Efficient Frontier") +
  labs(color='Factor Portfolios') +
  theme(plot.title= element_text(size=14, color="grey26",
  hjust=0.3,lineheight=2.4, margin=margin(15,0,15,0)), 
  panel.background = element_rect(fill="#f7f7f7"),
  panel.grid.major.y = element_line(size = 0.5, linetype = "solid", color = "grey"),
  panel.grid.minor = element_blank(),
  panel.grid.major.x = element_blank(),
  plot.background = element_rect(fill="#f7f7f7", color = "#f7f7f7"), 
  axis.title.y = element_text(color="grey26", size=12, margin=margin(0,10,0,10)),
  axis.title.x = element_text(color="grey26", size=12, margin=margin(10,0,10,0)),
  axis.line = element_line(color = "grey")) 
```
```{r}
# Calculate the TP
## HINT: Choose a similar risk free rate as in the exercise session. 
### import the risk-free data set
rf <- DATA3[,2]
### calculate the TP
mu_f = mean(rf)
## First the numerator and denominator 
numerator_T_N <- inv(cvar_ret) %*% (mean_ret - mu_f*rep(1, length(mean_ret)))
denominator_T_N <- t(rep(1, length(mean_ret)))%*%inv(cvar_ret)%*%(mean_ret - mu_f*rep(1, length(mean_ret)))
## calculate the weights
weights_T_N <- numerator_T_N[,1] / denominator_T_N
weights_T_N
return_T_N <- weights_T_N %*% mean_ret
sd_T_N <- sqrt(t(weights_T_N) %*% cvar_ret %*% weights_T_N)
```
```{r}
# Create the tangent portfolio

## HINT: What is the risk of the risk-free asset and the covariance of it with the risky asset(s)?
### define the risk of the risk-free asset and the covariance of it with risky assets
sigma_f = 0
sigma_Af = 0

## Define the sequence
x_tan = seq(from=-0.8, to=2.2, by=0.1)
x_f = 1 - x_tan

## Calculate the metrics
### Calculate the risk and return metrics
mu_T_N <- weights_T_N %*% mean_ret
sd_T_N <- sqrt(t(weights_T_N)%*%cvar_ret%*%weights_T_N)

### Create another dataframe
mu_sd_T_N_df <- as.data.frame(cbind(mu_T_N, sd_T_N))
colnames(mu_sd_T_N_df) <- c("mu_T_N", "sd_T_N")

mu_tanf = x_tan*mu_T_N + x_f*mu_f
var_tanf = x_tan^2*sd_T_N^2 + x_f^2*sigma_f^2 + 2*x_tan*x_f*sigma_Af
sd_tanf = sqrt(var_tanf)

# Only get the "positive returns" from the r_f on
mu_tanf_real <- mu_tanf[1:9]
sd_tanf_real <- sd_tanf[1:9]
# Create a df
cml_N <- as.data.frame(cbind(mu_tanf_real, sd_tanf_real))
colnames(cml_N) <- c("MU_CML", "SD_CML")
mu_sd_T_N_df
```

```{r}
port <- as.data.frame(cbind(Minimum_Variance = c(t(x_MV), mu_MV, sd_MV),
                            Tangency = c(weights_T_N, return_T_N, sd_T_N)))
rownames(port) <-c(colnames(asset_returns), "Return", "sd")
xtable(port, caption = "Weights of two portfolios", digits = 5)
```

